---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

title: "Time Series Research Assignment"
subtitle: "A Replication: Estimation of the Equilibrium Real Exchange Rate for South Africa [@mainpaper]"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: FALSE
# Entry1: "An unbelievable study with a title spanning multiple lines."
# Entry2: "\\textbf{Nico Katzke}" # textbf for bold
# Entry3: "A thesis submitted toward the degree of Doctor of Philosophy"
# Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
# Logo_width: 0.3 # If using a logo - use this to set width (size) of image
# Entry4: "Under the supervision of: \\vfill Prof. Joe Smith and Dr. Frank Smith"
# Entry5: "Stellenbosch University"
# Entry6: April 2020
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
Author1: "Jacques Rossouw - 21159793"  # First Author - note the thanks message displayed as an italic footnote of first page.
Ref1: "Stellenbosch, Western Cape, South Africa" # First Author's Affiliation
Email1: "gerardrossouw\\@gmail.com" # First Author's Email address

# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"
# 
# CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE
# 
# # Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
# BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
# Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: TRUE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: FALSE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Abstract to be written here.
---

<!-- First: Default preferences for chunk options: -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, 
                      fig.width = 6, fig.height = 5, fig.pos="H", 
                      fig.pos = 'H', purl = TRUE)
library(pacman)

pacman::p_load(tidyverse, dplyr, stargazer, readr, lubridate, vars, dynlm, 
               tsDym)
fmxdat::source_all("./code")
```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

\newpage

# Introduction


* What did I do?
This paper is a replication and critical evaluation of the research paper by 
@mainpaper.

* why did I do this?


# Literature Review


## What did the Authors do?


## Motivation
* Importance
* Methods
* Novel Contribution(s)


## Critical Evaluation
* Robustness checks/extensions


# Replication



# Importing and Cleaning the Data


## Importing the full dataset:


```{r}
full_df <- fetch_full()
full_df
```


## Wrangling the dataset


```{r}
full_df <- full_clean(full_df)
full_df
```


## Variable Names (SECTION TO BE DELETED)

```{r}
as_tibble(names(full_df))
```






## Plotting the Variables of Interest


### Plotting REERS:


```{r}
plot_endog1(full_df)
```



### Plotting the determinants of the Real Effective Exchange Rate:


```{r fig.width=7}

plot_endog2(df = full_df)

```


## VECM Model Estimation:

_Multiple ways to estimate VEC models:_

_First approach: ordinary least squares (yields accurate result) but does not allow to estimate the cointegrating relations among the variables._
_The estimated generalised least squares (EGLS) approach would be an alternative._

_Most popular estimator: MLE of Johansen (1995)_
_[In R: ca.jo function of the urca package of Pfaff (2008a)]_
_Alternatively, `VECM` of tsDyn package of Di Narzo et al. (2020)_

_Before VECM:_
_1. Determine lag order p -> Det. rank of CI matrix r_
_2. deterministic terms have to be specified._
_3. Choose lag order: est. the VAR in levels_
_4. Choose lag specification that minimises an Information criterion_



### Determine the Lag Order


```{r}
# var_aic <- 
    
```






```{r}
# 
# endog_df <- split_data_endog(full_df)
# exog_df <- split_data_exog(full_df)
# 
# 
# mod <- VECM(data = endog_df[,2:8], lag = 4, r = 1,
#            include = "const", estim = "ML", exogen = exog_df[,2:4])
# 
# mod_summ <- summary(mod)


# mod <- dynlm(full_df$LREERS ~ full_df$RIRR + full_df$LRGDPPCR + full_df$OPENY
#            + full_df$FBYA + full_df$NFAOFPY + full_df$LPR2COMM5
#            + full_df$DUMNFAOFPY + full_df$DUMRER1
#            + full_df$DUMRER2 + full_df$DUMFBYA + full_df$SDUMC1
#            + full_df$SDUMC2 + full_df$SDUMC3,
#            lag = 4,
#            include = "const", estim = "ML", exog
#            exogen = exog_df[,2:8])
```

```{r results='asis', message=F, comment='%', tidy=T}

# stargazer(mod_summ$model, header = FALSE)

```







<!-- # Data and Methodology -->

<!-- ## Plotting the Real Effective Exchange Rate -->


<!-- ```{r} -->
<!-- lreer_plot <- full_df %>% dplyr::select(date, LREERS) %>%  -->
<!--     ggplot() + -->
<!--     geom_line(aes(x = date, y = exp(LREERS)), col = "steelblue") + -->
<!--     labs(title = "South African Real Effective Exchange Rate") + -->
<!--     scale_y_continuous("Real Effective Exchange Rate") + -->
<!--     scale_x_date("Date") -->

<!-- lreer_plot -->
<!-- ``` -->



# Directly from [@mainpaper]





## Section 3 Data and Methodology

* Plotting the exp(LREER) and the rest of the variables
* Showcase the vector of interest
* Investigate LR CI Rel's amongst var's in vector
    - Method: MLE of @johansenMLE
    - Why? Corrects for Autocorr and ednog parametrically using VECM specif.
    - Key Advantage: the estimated coefficient - the $\beta$ vector - can be used to 
    provide a measure of the equilibrium real exchange rate and therefore a 
    quantification of the gap between the prevailing real exchange rate and 
    its equilibrium level. The methodology also derives estimates of the speed 
    at which the real exchange rates converges to the equilibrium level.


    






# Old Stuff

<!-- ## Log of Real Effective Exchange Rate for SA (LREER) -->

<!-- Importing the `LREER` time series: -->

<!-- ```{r} -->
<!-- # LREER <- lreer_fetch() -->
<!-- # # # check whetther there are any `NA` vales in the dataset -->
<!-- # # LREER %>% select(Value) %>% any(is.na(.)) -->
<!-- # LREER -->
<!-- ``` -->


<!-- cleaning the lreer dataset -->
<!-- ```{r} -->
<!-- # Convert the date column to the correct format -->
<!-- # LREER <- lreer_wrangle_date(LREER) -->
<!-- #  -->
<!-- # # And change the base year from 2015 to 1995 as in the paper -->
<!-- # LREER <-lreer_rebase(LREER) -->
<!-- # LREER -->
<!-- ``` -->



<!-- ## Real Interest Rate Relative to Trading Partners -->

<!-- ```{r} -->
<!-- # RIRR <- rirr_fetch() -->
<!-- # RIRR -->
<!-- ``` -->


